Forcing for Isabelle

### 2018-12-19 LICS/zfc-axioms.tex
ed. varias, esp. Hacking y comentario para Miguel

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%          
\section{Axioms and models of set theory}

@@

compatible with the development of relativization by Paulson. For

@@

above $\psi$). Thanks to Pairing, these

@@

%
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Separation_In_MG"
%%% ispell-local-dictionary: "american"
%%% End:

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%          
\section{Axioms and models of set theory}
\label{sec:axioms-models-set-theory}

@@

compatible with the development by Paulson. For

@@

above $\psi$), where \isatt{sats\,::\,"[i,i,i]=>o"} is the satisfaction
relation between a set model with an environment and an internalized
formula. Thanks to Pairing, these 

@@

It is also possible define a predicate that states that a set
satisfies a (possibly infinite) set of formulas, and then to state
that ``$M$ satisfies $\ZF$'' in a standard way. With the
aforementioned restriction on parameters, it can be shown that this
statement is equivalent to the set of assumptions of the locale
\isatt{M\_ZF}.
%
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "Separation_In_MG"
%%% ispell-local-dictionary: "american"
%%% End:
